### 2014-03-28 LaTeX/RhodiumEmp.tex
more maps
more stuff

\begin{figure}[ht]
	\centering
	\includegraphics[width=.9/textwidth]{CityConfMap-crop}
	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008. Countries for which no armed conflicts are recorded are shaded in grey.}
	\label{fig:CityConfMap}
\end{figure}

We restrict our sample to only those countries that are listed as having conflicts in the PRIO dataset. Specifically, this means that our analysis focuses on exploring variations in economic growth among countries currently engaged in internal armed conflict by the proximity of those conflicts to major cities. To do this we first calculate the distance between the centroid of each of the conflicts identified in the PRIO armed conflict dataset with the centroids of the city locations. Doing this between every city and every conflict

>>>>

\begin{figure}[ht]
	\centering
	\includegraphics[width=.9\textwidth]{CityConfMap-crop}
	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008. Countries for which no armed conflicts are recorded are shaded in grey.}
	\label{fig:CityConfMap}
\end{figure}

We restrict our sample to only those countries that are listed as having conflicts in the PRIO dataset. Specifically, this means that our analysis focuses on exploring variations in economic growth in countries undergoing conflict by the proximity of those conflicts to major cities. To do this we first calculate the distance between the centroid of each of the conflicts identified in the PRIO armed conflict dataset with the centroids of the city locations. We calculate the

\begin{figure}[ht]
	\centering
	\includegraphics[width=.7\textwidth]{colombiaMap-crop}
	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008. Countries for which no armed conflicts are recorded are shaded in grey.}
	\label{fig:CityConfMap}
\end{figure}
